Discrete and continuous latent states of neural activity in \textit{Caenorhabditis Elegans}

### 2016-07-29 drafts/writeup_07_25_16.tex
refactoring, adding notebooks

\begin{figure}[t]
\centering%
\includegraphics[width=5.5in]{slds} 
\caption{Simulated data from a switching linear dynamical system.
The population stochastically jumps between discrete states,~$z_t \in \{a,b,c,d\}$,
each of which is color coded for visualization.
These discrete states govern the linear dynamics of the continuous latent 
state,~$\bx_t \in \reals^D$ (here,~$D=2$). For example, state~$a$ corresponds to a simple
random walk, whereas state~$d$ has fast, oscillatory dynamics. Finally,
the observed signals,~$\by_t \in \reals^N$ (here,~$N=8$), are obtained via a linear 
transformation of the underlying, continuous state,~$\bx_t$. The correlations
and dynamics in the observations are inherited from the dynamics of the
latent states.}
\vspace{-0.5cm}
\label{fig:slds_ex}
\end{figure}

>>>>

\begin{figure}[t]
\centering%
\includegraphics[width=5.5in]{slds} 
\caption{Simulated data from a switching linear dynamical system.  The
  population stochastically switches between discrete states,~$z_t \in
  \{1,\ldots,K\}$ (here,~$K=5$), each of which is color coded for
  visualization.  These discrete states govern the linear dynamics of
  the continuous latent state,~$\bx_t \in \reals^D$ (here,~$D=2$). For
  example, state~$z_t=1$ corresponds to a simple random walk, whereas
  state~$z_t=5$ has fast, oscillatory dynamics. Finally, the observed
  signals,~$\by_t \in \reals^N$ (here,~$N=8$), are obtained via a
  linear transformation of the underlying, continuous
  state,~$\bx_t$. The correlations and dynamics in the observations
  are inherited from the dynamics of the latent states.}
\vspace{-0.5cm}
\label{fig:slds_ex}
\end{figure}
